%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% Version: 20110122-4


\documentclass[11pt,a4paper,nolmodern]{moderncv}

\usepackage{WeizhouPan}
\usepackage{amsmath, amssymb, latexsym}
\usepackage[english]{babel}
\linespread{0.8}

% personal data
\title{Weizhou Pan, SDET}
\address{\href{www.baidu.com}{Baidu\texttrademark}}{}
\extrainfo{\octocat~\url{http://github.com/wzpan}\\
\linkedin~\httplink{www.linkedin.com/in/hahack}%
}
%\myquote{\href{http://www.hahack.com}{www.hahack.com}}{}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\setmainfont{Minion Pro}
\setsansfont{Myriad Pro}

\hyphenpenalty=10000
\maketitle

\section{Skills}

\cvcomputer{Languages}{C/C++, Python, Shell/Bash}
           {Operating Systems}{Linux, Windows, Mac}
\cvcomputer{English Proficiency}{CET6(513)}
           {Development Tools}{Emacs, Git, Makefile, gdb, Valgrind}
\cvcomputer{Documentation}{\LaTeX{}, Doxygen, Markdown}
           {Unit Test}{minunit, nose, doctest}

\section{Experience}

\subsection{Career Experience}

\tlcventry{2014}{0}{\href{http://www.baidu.com/}{Baidu\texttrademark}}{Software Development Engineer in Test}{}{}
{
\begin{tightitemize}%
 \item Main developer for \href{http://godeyes.duapp.com}{GodEyes-iOS}, a static
   language crash analyzer for iOS APP. (Users includes \href{http://www.baidu.com}{Baidu\texttrademark},
   \href{http://www.taobao.com}{Alibaba\texttrademark}, \href{http://www.qq.com}{Tencent\texttrademark}, \href{http://jd.com}{Jingdong\texttrademark}, \textsl{etc.})
 \item Attended testing for Baidu Navi project. Wrote foundation tools for
   map testing \textsl{e.g.} map format checker, svn
   watcher, flow analyzer, \textsl{etc.}, which motivated
   the map testing automation rate to 100\%.
 \end{tightitemize}}

\subsection{Scientific Experience}

\tlcventry{2013}{2012}{\href{http://www.siat.ac.cn/}{Shenzhen
    Institute of Advanced Technology}}{Intern Student}{}{}
{Doing scientific research.
\begin{tightitemize}%
 \item Studied texture weathering, motion clustering, shape retrieval, etc.
 \item Published 5 papers. Applied 1 Patent.
 \item Gained intern student scholarships. 
 \end{tightitemize}}

\subsection{Open-source Experience}

\tlcventry{2014}{2013}{\href{http://github.com/wzpan/qtevm}{QtEVM}}{Author}{}{}%
  {
\begin{itemize}
\item \textbf{Abstract}: Open source implementation for \href{http://people.csail.mit.edu/mrub/vidmag/}{EVM(Eulerian Video Magnification)}.
\item \textbf{Features}: The first open-source completed C++ implementation for EVM, which supports both motion and color magnification.
\item \textbf{Stats}: 10 stars, 2 forks.
\end{itemize}}

\tlcventry{2013}{2012}{\href{http://github.com/wzpan/scnuthesis}{SCNUThesis}}{Author}{}{}%
  {
\begin{itemize}
\item \textbf{Abstract}: Dissertation LaTeX Template for Sourth China Normal
  University.
\item \textbf{Features}: Supports both master and doctor dissertations, with lots of options for easily customizing.
\item \textbf{Stats}: 16 stars, 6 forks, 2,000+ downloads. Helped lots of
  student finish their dissertations.
\end{itemize}}

\tlcventry{2014}{2013}{\href{http://github.com/wzpan/hexo-theme-freemind}{hexo-theme-freemind}}{Author}{}{}%
  {
\begin{itemize}
\item \textbf{Abstract}: One of the most popular theme for \href{hexo.io}{Hexo}.
\item \textbf{Features}: Luxuriant tag plugins so as to get the power of Twitter Bootstrap with minimal hassle.
\item \textbf{Stats}: 50 stars, 28 forks.
\end{itemize}}

\section{Awards}

% Restore normal labels
%\tltext{\scriptsize}

{

\tldatelabelcventry{2013}{2013.10}{National Scholarship}{South
  China Normal University}{}{}{}

\setlength{\parskip}{-20pt}

\tldatelabelcventry{2011}{2011.10}{Silver Prize}{the 12th Challenge Cup of
  National College Students' Academic Works}{}{}{}

\tldatelabelcventry{2011}{2011.6}{Outstanding Graduate \& Dissertation}{South
  China Normal University}{}{}{}

\setlength{\parskip}{-10pt}

\tlcventry{2012}{2008}{1st Grade Scholarship($\times$ 2), 2nd
  Grade Scholarship($\times$ 2), Innovation Scholarship}{South China
  Normal University}{}{}{}

}

% Publications from a BibTeX file without multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% for BibTeX numerical labels
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}   % 'publications' is the name of a BibTeX file

\end{document}

